|

### 2021-10-20 07-Chp-Triangulation.Rmd
End of day
End of day:

@@

Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and

>>>>

### Qualitative triangulation

<!-- TODO Need to talk about fibrates here too -->

__Statins and all-cause dementia__

This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`). Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.

Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].

&nbsp;

__Statins and Alzheimer's disease__

Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease. No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings. Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]

Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]

&nbsp;

__Statins and vascular/other dementia__

Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias. A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`). When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.

&nbsp;

__Other drug classes__

Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).

One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.

A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings. Note that this study was published in 2020 and so was not included in the review.

@@

Table with columns describing exposure, outcome, time-point, other aspects (cumulative), and

### 2021-10-20 manuscripts/cprd/manuscript.Rmd
End of day:

* Main text word count (max 4000): 3104
* Abstract word count (max 250): 250

@@

This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee. The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on GitHub (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of publication on Zenodo (DOI: __TBC__).

@@

_Figure 1: Results from the primary analyses of CPRD data comparing prescription of an lipid-regulating drug with no prescription, stratified by dementia outcome and drug class. All results were obtained using the fully adjusted model and participant age as the time scale._

>>>>

* Main text word count (max 4000): 3442
* Abstract word count (max 250): 250

@@

This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee. The code lists used to define the outcomes and covariates for this study are available as a supplementary file. The code lists, as well as the scripts used to create the study cohort and perform the analyses, are also available from the GitHub repository for this project (https://github.com/mcguinlu/CPRD-LRA), which was archived at the time of publication on Zenodo (DOI: __TBC__).

@@

_Figure 1: Results from the primary analyses of CPRD data comparing prescription of a lipid-regulating drug with no prescription, stratified by dementia outcome and drug class. All results were obtained using the fully adjusted model and participant age as the time scale._

### 2021-10-20 tmp.Rmd
End of day:

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/03-Code-Systematic-Review.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/helper.R")
knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model. The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while otherss were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]

(ref:covariateDef-scaption) Covariates adjusted for.

(ref:covariateDef-cell1) Charlson index implemented using Read code lists.[@khan2010] Code lists based on those by Taylor et al.[@taylor2016]

(ref:covariateDef-cell2) Most recent of recorded value (current, former or never) or Read code indicating a recorded value. Code lists based on those by Wright et al.[@wright2017]

```{r covariateDef-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
